Naturalness in U(1) extensions of the MSSM

### 2015-01-21 paper/e6ssm-tuning-paper.tex
Added part of the table for the benchmark parameter values

To further illustrate this point we looked at how the tuning varies
with $M_X$ for low tuning benchmarks in the MSSM and E$_6$SSM. These
benchmarks are defined in table \ref{} and the results are shown in
Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is quite complicated we
now discuss these in detail as it provides some insight into the many
differences in the tuning between the two models.

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_all_benchmark_points_tuning_vs_cutoff.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
\caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in (?).  {\it Top right panel:}  Individual sensitivites of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.  {\it Bottom left panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.  {\it Bottom right panel:} Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}

>>>>

To further illustrate this point we looked at how the tuning varies
with $M_X$ for low tuning benchmarks in the MSSM and E$_6$SSM. These
benchmarks are defined in Table \ref{tab:benchmarks} and the results are shown in
Fig.~\ref{Fig:BMs-varyMX}. Since the behaviour is quite complicated we
now discuss these in detail as it provides some insight into the many
differences in the tuning between the two models.

\begin{table}[h]
\centering
\begin{ruledtabular}
\begin{tabular}{cccc}
& MSSM & E$_6$SSM BM1 & E$_6$SSM BM2 \\
\hline
$\tan\beta(M_Z)$ & 10 & 10 & 10 \\
$s(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 6700 & 6700 \\
$\mu_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 689.7 & 1093.3 & -1093.3 \\
$B_{\mathrm{eff}}(M_{\mathrm{SUSY}})$ [GeV] & 345.7 & 3792.7 & -3792.7 \\
$A_t(M_{\mathrm{SUSY}})$ [GeV] & -3335.7 & -1100 & -3335.7 \\
$m_{Q3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4.45379310\times 10^6$ & $4.49655\times 10^5$ & $6.5\times 10^5$ \\
$m_{u3}^2(M_{\mathrm{SUSY}})$ [GeV$^2$] & $4\times 10^6$ & $5.86207\times 10^5$ & $4.5\times 10^5$ \\
$M_1(M_{\mathrm{SUSY}})$ [GeV] & 300 & 300 & 300 \\
$M_2(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 1050 & 2000 \\
$M_3(M_{\mathrm{SUSY}})$ [GeV] & 2000 & 2000 & 1200 \\
$M_1^\prime(M_{\mathrm{SUSY}})$ [GeV] & $-$ & 300 & 300 \\
\hline
$m_{h_1}$ [GeV] & 124.3 & 125.0 & 124.9 \\
$m_{\tilde{g}}$ [GeV] & & 2290.0 & 1453.8\\
\hline
$\Delta(M_X=20\textrm{ TeV})$ & 157.3 & 165.3 & 228.5 \\
$\Delta(M_X=10^{16}\textrm{ GeV})$ & 1089.0 & 1722.3 & 917.6
\end{tabular}
\end{ruledtabular}
\caption{Parameters and masses for the MSSM point and the E$_6$SSM benchmark points 
BM1 and BM2 for which the fine tuning as a function of cutoff scale is studied. For the
E$_6$SSM benchmarks we define $\mu_{\mathrm{eff}}\equiv \lambda s/\sqrt{2}$ and
$B_{\mathrm{eff}}=A_\lambda$.}
\label{tab:benchmarks}
\end{table}

\begin{figure}
\begin{center}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_mssm_cutoff_scan_all_benchmark_points_tuning_vs_cutoff.png}} 
\resizebox{!}{5.5cm}{%
\includegraphics{mssm_cutoff_scan_tb10_fixed_at_ms_all_tuning_data.png}} 
\\
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM1_all_tuning_data.png}}
\resizebox{!}{5.5cm}{%
\includegraphics{e6ssm_light_zprime_cutoff_scan_tb10_BM2_all_tuning_data.png}}%%
\caption{{\it Top left panel:} Scatter plot of fine tuning vs high scale $M_X$ for the three benchmark points given in Table \ref{tab:benchmarks}.  {\it Top right panel:}  Individual sensitivites of the MSSM benchmark plotted against the high scale $M_X$ which give an overall tuning shown by the green line in top left panel.  {\it Bottom left panel:} Individual sensitivites of E6SSM BM1 plotted against the high scale $M_X$ which give an overall tuning shown by the blue line in top left panel.  {\it Bottom right panel:} Individual sensitivites of E6SSM BM2 plotted against the high scale $M_X$ which give an overall tuning shown by the red line in top left panel.    }
\label{Fig:BMs-varyMX}
\end{center}
\end{figure}
